Turbulence in compact to giant HII regions

### 2021-12-07 strucfunc_paper.tex
New first paragraph of introduction

@@

We use data from \citet{arthur2016turbulence} to study of turbulence in the Orion Nebula.
Their observations were initially published by \citet{2008RMxAA..44..181G}. 
The data was obtained with the echelle spectrograph attached to the 4 m telescope at Kitti Peak National Observatory (KPNO).
These observation cover 3 \(\times\) 5 arcmin\(^{2}\) of the central (Huygens) part of the Orion nebula.
The data consist of 96, North-South orientated 300 arcsec slits at 2 arcsec intervals with a width of 0.8 arcsec with a velocity resolution of 8 km s\(^{-1}\).

@@

The second-order structure function of the velocity centroids, $B(r)$, is defined as:

\begin{equation}\label{eq:Br}
B(\boldsymbol{r}) = \dfrac{\sum_{\text{pairs}}[V_{c}(\boldsymbol{x} + \boldsymbol{r}) - V_{c}(\boldsymbol{x}) ]^{2}} {N(\boldsymbol{r})}
\end{equation}
%
where $N(\boldsymbol{r})$ is the number of pair points at each separation \(\boldsymbol{r}\), called lag. 
In the Kolmogorov model \(B(r) \propto r^{2/3}\).

The variance of the centroid velocity fluctuations is:

\begin{equation}\label{eq:variance}
\sigma^2  = \frac{\sum_{\text{pixels}}[ V_c (\boldsymbol{x}) -\langle V_ c\rangle  ]^2}{N}
\end{equation}
%
the, \(\langle V_c \rangle \) is the mean centroid velocity

\begin{equation}\label{eq:mean}
\langle V_c \rangle \  = \frac{\sum_{\text{pixels}}[ V_c (\boldsymbol{x})]}{N}
\end{equation}
%
The summation in Equation \ref{eq:Br} is over all data pairs for each separation \(N(\boldsymbol{r})\).
The summations in Equations \ref{eq:variance} and \ref{eq:mean} are over the total number of valid pixels in the (\textit{x},\textit{y})-plane.

@@

\citet{2012MNRAS.422.3339W} have found that clumps and HII regions follow scaling relations over the range of z = 0-2 for \halpha\ size, velocity dispersion, luminosity and mass, finding \(\sigma \propto r^{0.42}\), \(\text{L}_{\text{H}_{\alpha}} \propto r^{2.72}\) and \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4.18}\), respectively. 
This results imply that the same process are seen at high redshifts and the current epoch in star forming regions.
Recently, \citet{2015MNRAS.449.3568M} found that the relation in dwarf galaxies is \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{5}\).
\citet{2018MNRAS.474.1250F} presented the relationship between integrated H$_{\beta}$ line luminosity and the velocity dispersion for new data of 36 giant HII regions obtaining \(\text{L}_{\text{H}_{\beta}} \propto \sigma^{5.02 \pm 0.21}\).

>>>>

Photoionized regions around high-mass stars (\hii{} regions)
show highly vigorous dynamics
as a result of the star formation process and the energy and momentum
injected by the newly-formed stars.
Rather than manifesting a simple pattern such as expansion, infall, or rotation,
the motions are frequently disordered or ``turbulent''
and must be characterised by statistical techniques.
In relatively low luminosity regions, such as the nearby Orion Nebula,
the disordered motions are approximately transonic,
with typical velocities of order \num{5} to \SI{10}{km.s^{-1}}
\citep{castaneda1988, Garcia-Diaz:2008a}.
In larger, higher luminosity regions,
such as 30~Doradus in the Large Magellanic Cloud,
the velocities are significantly supersonic,
of order \SI{30}{km.s^{-1}} \citep{Torres-Flores:2013t, Castro:2018a}.
The same tendency of increasing velocity dispersion (\(\sigma\))
and luminosity (\(L\))
continues up to the scale of entire galaxies
with an approximate relation \(L \propto \sigma^n\) that spans
more than 5 orders of magnitude in luminosity
with a  power-law index \(n = 3\) to~\(7\)
\cite{Rozas:2006b, Moiseev:2015a}.
However, it is unclear whether a single physical mechanism
underlies this relationship at all scales.
The relative importance of gravity and the various stellar feedback mechanisms
(heating, direct radiation pressure, stellar winds, cluster winds)
are unclear in many cases and are frequently disputed \citep{Krumholz:2016a, Melnick:2021x}.

@@

We use data from \citet{arthur2016turbulence} to study of turbulence in the Orion Nebula.
Their observations were initially published by \citet{Garcia-Diaz:2008a}. 
The data was obtained with the echelle spectrograph attached to the 4 m telescope at Kitti Peak National Observatory (KPNO).
These observation cover 3 \(\times\) 5 arcmin\(^{2}\) of the central (Huygens) part of the Orion nebula.
The data consist of 96, North-South orientated 300 arcsec slits at 2 arcsec intervals with a width of 0.8 arcsec with a velocity resolution of 8 km s\(^{-1}\).

@@

The second-order structure function of the velocity centroids, $B(r)$, is defined as:
%
\begin{equation}\label{eq:Br}
  B(\boldsymbol{r}) = \dfrac{1}{N(\boldsymbol{r})}
  \,
  \sum_{\text{pairs}} \bigl[
  V_{c}(\boldsymbol{x} + \boldsymbol{r}) - V_{c}(\boldsymbol{x})
  \bigr]^{2}
\end{equation}
%
where $N(\boldsymbol{r})$ is the number of pair points at each separation \(\boldsymbol{r}\), called lag. 
In the Kolmogorov model \(B(r) \propto r^{2/3}\).

The variance of the centroid velocity fluctuations is:
%
\begin{equation}\label{eq:variance}
\sigma^2  = \frac{1}{N} \sum_{\text{pixels}} \bigl[ V_c (\boldsymbol{x}) -\langle V_ c\rangle  \bigr]^2
\end{equation}
%
the, \(\langle V_c \rangle \) is the mean centroid velocity
%
\begin{equation}\label{eq:mean}
\langle V_c \rangle \  = \frac{1}{N} \sum_{\text{pixels}} V_c (\boldsymbol{x})
\end{equation}
%
The summation in Equation \ref{eq:Br} is over all data pairs for each separation \(N(\boldsymbol{r})\).
The summations in Equations \ref{eq:variance} and \ref{eq:mean} are over the total number of valid pixels in the (\textit{x},\textit{y})-plane.

@@

\citet{2012MNRAS.422.3339W} have found that clumps and HII regions follow scaling relations over the range of z = 0-2 for \halpha\ size, velocity dispersion, luminosity and mass, finding \(\sigma \propto r^{0.42}\), \(\text{L}_{\text{H}_{\alpha}} \propto r^{2.72}\) and \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4.18}\), respectively. 
This results imply that the same process are seen at high redshifts and the current epoch in star forming regions.
Recently, \citet{Moiseev:2015a} found that the relation in dwarf galaxies is \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{5}\).
\citet{2018MNRAS.474.1250F} presented the relationship between integrated H$_{\beta}$ line luminosity and the velocity dispersion for new data of 36 giant HII regions obtaining \(\text{L}_{\text{H}_{\beta}} \propto \sigma^{5.02 \pm 0.21}\).
